---
title: "SOL BDA Window Selection Analysis & Simulations"
author: "Kyle MacDonald"
date: "April 14, 2016"
output: html_document
---

In this document, you will find the details of our simulations for the analysis models in the paper, "Real-time Language Comprehension in American Sign Language." Specifically, we fit our models to three different analysis windows to show that our parameter estimates of the association between age/vocab and accuracy/RT are robust to this decision. 

Input: tidy data summarizing mean accuracy and RT scores for each participant
Output: tidy data with posterior samples from 4 models each fit to 3 different analysis windows with 3 different specifications for the width of the prior distribution on the slope parameter

## Load packages, data, and some helpful functions

```{r, echo = F}
rm(list=ls()) # clear workspace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T, warning=F, message=F, 
                      results = "hide")

source("../../helper_functions/useful.R")

library(langcog); library(knitr); 
library(polspline); library(rethinking); 
library(R2jags); library(rjags); 
library(magrittr); library(tidyverse); 
library(car)
```

Set the seed so we can reproduce the exact simulations.

```{r}
set.seed(13412)
```


```{r load data}
# Load data
d_2200 <- read.csv("../../../data/processed_data/summary_tables/sol_ss_all_600_2200.csv")
d_2500 <- read.csv("../../../data/processed_data/summary_tables/sol_ss_all_600_2500.csv")
d_2800 <- read.csv("../../../data/processed_data/summary_tables/sol_ss_all_600_2800.csv")

d_2200$window <- "600_2200"
d_2500$window <- "600_2500"
d_2800$window <- "600_2800"

# Merge data from different analysis windows
d <- bind_rows(d_2200, d_2500, d_2800)
```

```{r}
d %>% 
  filter(age_group_collapsed == "Kids") %>% 
  select(Sub.Num) %>% 
  unique() %>% 
  nrow()
```

Following Barr (2008), we use a logit transform to convert the accuracy scores which are on a proportion scale to a log odds scale to be more suitable for the linear model.

```{r}
d %<>% mutate(logit_acc = car::logit(mean_prop_looking_TD))
```


Standardize the data

```{r}
d %<>% mutate(C_D_count = ifelse(is.na(C_D_count), 0, C_D_count),
              total_trials_shifting = C_T_count + C_D_count,
              Sub.Num = as.character(Sub.Num)) %>% 
  dplyr::select(Sub.Num, age_peek_months, age_group, signs_produced, 
                C_T_count,total_trials_shifting,
                median_rt = median_ct_rt, 
                C_T_prop, logit_acc, mean_prop_looking_TD,
                value_cat, age_group_collapsed, hearing_status_participant, window)

d_all <- d %>% filter(value_cat == "Target" | value_cat == "Distractor")    
```

```{r}
d %<>% filter(age_group_collapsed == "Kids", value_cat == "Target")  %>% 
  mutate(age.s = (age_peek_months - mean(age_peek_months, na.rm=T)) / sd(age_peek_months, na.rm=T),
         acc.s.logit = (logit_acc - mean(logit_acc)) / sd(logit_acc),
         acc.s = (logit_acc - mean(logit_acc)) / sd(logit_acc),
         rt.s = (median_rt - mean(median_rt)) / sd(median_rt),
         voc.s = (signs_produced - mean(signs_produced)) / sd(signs_produced),
         hearing_status_dummy = ifelse(hearing_status_participant == "deaf", 1, 0))
```

```{r}
d_voc <- d %>% 
  filter(is.na(signs_produced) == F) %>% 
  mutate(age.s = (age_peek_months - mean(age_peek_months, na.rm=T)) / sd(age_peek_months, na.rm=T),
         acc.s.logit = (logit_acc - mean(logit_acc)) / sd(logit_acc),
         acc.s = (mean_prop_looking_TD - mean(mean_prop_looking_TD)) / sd(mean_prop_looking_TD),
         rt.s = (median_rt - mean(median_rt)) / sd(median_rt),
         voc.s = (signs_produced - mean(signs_produced, na.rm = T)) / sd(signs_produced, na.rm = T),
         hearing_status_dummy = ifelse(hearing_status_participant == "deaf", 1, 0))
```

```{r}
d %>% 
  filter(age_group_collapsed == "Kids") %>% 
  select(Sub.Num) %>% 
  unique() %>% 
  nrow()
```

Save output.

```{r, eval = F}
write.csv(d, file = "../../../data/processed_data/summary_tables/sol_ss_dage_models.csv", row.names = F)
write.csv(d_voc, file = "../../../data/processed_data/summary_tables/sol_ss_dvoc_models.csv", row.names = F)
```

Subset data by each analysis window.

```{r subset data by analysis window}
d_2200 <- filter(d, window == "600_2200")
d_2500 <- filter(d, window == "600_2500")
d_2800 <- filter(d, window == "600_2800")
d_voc_2200 <- filter(d_voc, window == "600_2200")
d_voc_2500 <- filter(d_voc, window == "600_2500")
d_voc_2800 <- filter(d_voc, window == "600_2800")
```

All models fit using JAGS [@plummer2003jags] and based on models from Ch. 17 in @kruschke2014doing. 

First, we need to set the parameters for the MCMC simulations. This will be the same 
across all models. The key parameter of interest is the standardized slope: zbeta1.
This encodes the strength of the linear relationship between the predictor variable
and the outcome.

# Analysis 1: Accuracy Model and simulations

```{r set parameters for accuracy model}
adaptSteps = 500  # Number of steps to "tune" the samplers
nChains = 3 
thinSteps = 1
numSavedSteps = 21000
nIter = ceiling( ( numSavedSteps * thinSteps ) / nChains )
burnInSteps = nIter / 2
parameters = c( "zbeta0" , "zbeta1" , "zsigma" , "zbeta1_prior" , "zbeta0_prior" )
```

```{r}
# make list of  data frames to loop over
dfs <- list(d_2200, d_2500, d_2800)
dfs_voc <- list(d_voc_2200, d_voc_2500, d_voc_2800)
```

```{r age_acc simulations}
slope_priors <- c(.1, .5, 1, 2)

df_acc_age_final <- window_simulations_fun(list_of_dfs = dfs_voc, 
                                           predictor = "age.s", outcome = "acc.s.logit", 
                                           model_type = "accuracy",
                                           prior_list = slope_priors)

df_acc_voc_final <- window_simulations_fun(list_of_dfs = dfs_voc, 
                                           predictor = "voc.s", outcome = "acc.s", 
                                           model = "accuracy",
                                           prior_list = slope_priors)
```

Inspect chains for convergence and see any differences across windows.

```{r}
a <- df_acc_age_final %>% 
  sample_n(., size = 2000) %>% 
  ggplot(aes(x=iteration, y=beta1), data = .) + 
  geom_line() +
  ggtitle("Trace of Slope Parameter for Accuracy ~ Age") +
  facet_grid(slope_prior~window)  +
  scale_color_solarized() +
  xlab("Iteration Number") +
  guides(color = F)

b <- df_acc_voc_final %>% 
  sample_n(., size = 2000) %>%
  ggplot(aes(x=iteration, y=beta1), data = .) + 
  geom_line() +
  ggtitle("Trace of Slope Parameter for Accuracy ~ Vocab") +
  facet_grid(slope_prior~window)  +
  scale_color_solarized() +
  xlab("Iteration Number") +
  guides(color = F)

gridExtra::grid.arrange(a, b, ncol = 2)
```

Get means and 95% HDIs.

```{r}
df_acc_age_final %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            lower = HDIofMCMC(beta1)[1],
            upper = HDIofMCMC(beta1)[2])

df_acc_voc_final %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            lower = HDIofMCMC(beta1)[1],
            upper = HDIofMCMC(beta1)[2])
```

Save data frames with posterior samples for all three analysis windows for later analysis.

```{r, eval = F}
write.csv(x = df_acc_age_final, "simulations/diff_windows/sol_acc_age_mcmc.csv", row.names = F)
write.csv(x = df_acc_voc_final, "simulations/diff_windows/sol_acc_voc_mcmc.csv", row.names = F)
```

# Analysis 2: RT Model and simulations

Set parameters to monitor and initial values for each RT model.

```{r set params for rt model}
parameters = c( "true_beta0" , "true_beta1", "true_beta0_prior", "true_beta1_prior", "z")
myinits <-  list(
  list(phi = 0.75, z = round(runif(length(d_2200$age.s)))),
  list(phi = 0.5, z = round(runif(length(d_2200$age.s)))),
  list(phi = 0.99, z = round(runif(length(d_2200$age.s))))
)
```

Draw samples from all three analysis windows.

```{r}
slope_priors <- c(.1, .5, 1, 2)
df_rt_age_final <- window_simulations_fun(list_of_dfs = dfs_voc, 
                                          predictor = "age.s", outcome = "rt.s", 
                                          model = "rt",
                                          prior_list = slope_priors)


df_rt_voc_final <- window_simulations_fun(list_of_dfs = dfs_voc, 
                                          predictor = "voc.s", outcome = "rt.s", 
                                          model = "rt",
                                          prior_list = slope_priors)
```

Inspect chains for convergence and see any differences across windows and priors.

```{r}
a <- df_rt_age_final %>% 
  sample_n(., size = 2000) %>% 
  ggplot(aes(x=iteration, y=beta1), data = .) + 
  geom_line() +
  ggtitle("Trace of Slope Parameter for RT ~ Age") +
  facet_grid(slope_prior~window)  +
  scale_color_solarized() +
  xlab("Iteration Number") +
  guides(color = F)

b <- df_rt_voc_final %>% 
  sample_n(., size = 2000) %>% 
  ggplot(aes(x=iteration, y=beta1), data = .) + 
  geom_line() +
  ggtitle("Trace of Slope Parameter for RT ~ Vocab") +
  facet_grid(slope_prior~window)  +
  scale_color_solarized() +
  xlab("Iteration Number") +
  guides(color = F)

gridExtra::grid.arrange(a, b, ncol = 2)
```

Get means and 95% HDIs.

```{r}
df_rt_age_final %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            lower = HDIofMCMC(beta1)[1],
            upper = HDIofMCMC(beta1)[2])

df_rt_voc_final %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            lower = HDIofMCMC(beta1)[1],
            upper = HDIofMCMC(beta1)[2])
```

Save MCMC output.

```{r}
write.csv(x = df_rt_age_final, "simulations/sol_rt_age_mcmc.csv", row.names = F)
write.csv(x = df_rt_voc_final, "simulations/sol_rt_voc_mcmc.csv", row.names = F)
```