---
title: "SOL BDA Extra Simulations"
author: "Kyle MacDonald"
output: html_document
---

In this document, we present a brief analysis and visualization of the latent mixture component of our bayesian data analysis model. Specifically, we show posterior distributions over the indicator variable assigning each participant to the "guessing" or the "knowledge" group.

```{r chunk options, echo = F}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T, warning=F, message=F, 
                      results = "hide")

source("../../helper_functions/useful.R")

library(langcog); library(knitr); library(R2jags);
library(polspline); library(magrittr);
library(tidyverse)

theme_set(theme_classic())
```

Load data.

```{r load data}
d <- read.csv("../../../data/processed_data/summary_tables/sol_ss_dage_models.csv", 
              stringsAsFactors = F)

d_voc <- read.csv("../../../data/processed_data/summary_tables/sol_ss_dvoc_models.csv", 
                  stringsAsFactors = F)
```

Subset data by each analysis window.

```{r subset data by analysis window}
d_2200 <- dplyr::filter(d, window == "600_2200")
d_2500 <- dplyr::filter(d, window == "600_2500")
d_2800 <- dplyr::filter(d, window == "600_2800")
d_voc_2200 <- dplyr::filter(d_voc, window == "600_2200")
d_voc_2500 <- dplyr::filter(d_voc, window == "600_2500")
d_voc_2800 <- dplyr::filter(d_voc, window == "600_2800")
```

```{r}
# make list of  data frames to loop over
dfs <- list(d_2200, d_2500, d_2800)
dfs_voc <- list(d_voc_2200, d_voc_2500, d_voc_2800)

# set path to model files
model_path <- "models/"
```


```{r}
adaptSteps = 500  # Number of steps to "tune" the samplers
nChains = 3 
thinSteps = 1
numSavedSteps = 21000
nIter = ceiling( ( numSavedSteps * thinSteps ) / nChains )
burnInSteps = nIter / 2
parameters = c( "zbeta0" , "zbeta1", "zbeta1_prior", "zbeta0_prior")
```

### RT and age no latent mixture

Draw samples from all three analysis windows.

```{r}
slope_priors <- c(.1, .5, 1, 2)
df_rt_age_final <- window_simulations_fun_no_mix(list_of_dfs = dfs_voc, 
                                          predictor = "age.s", outcome = "rt.s", 
                                          model = "rt_no_mix",
                                          prior_list = slope_priors,
                                          path = model_path)


df_rt_voc_final <- window_simulations_fun_no_mix(list_of_dfs = dfs_voc, 
                                           predictor = "voc.s", outcome = "rt.s", 
                                           model = "rt_no_mix",
                                          prior_list = slope_priors,
                                          path = model_path)
```

Get means and 95% HDIs.

```{r}
df_rt_age_final %>% 
    group_by(window, slope_prior) %>% 
    summarise(mean = mean(beta1),
              lower = HDIofMCMC(beta1)[1],
              upper = HDIofMCMC(beta1)[2])

df_rt_voc_final %>% 
    group_by(window, slope_prior) %>% 
    summarise(mean = mean(beta1),
              lower = HDIofMCMC(beta1)[1],
              upper = HDIofMCMC(beta1)[2])
```

### Output of latent mixture models inferring guessing probability

```{r}
dataList_lat_mix = list(
    n_correct = d_2500$C_T_count,
    n_trials = d_2500$total_trials_shifting,
    Ntotal = length(d_2500$acc.s)
)

myinits <-  list(list(phi = 0.75, z = round(runif(length(d_2500$total_trials_shifting)))))

parameters <- c("z")

samples_post <- jags(data = dataList_lat_mix, parameters.to.save = parameters,
                model.file = paste(model_path, "latent_mixture.txt", sep = ""), 
                n.chains=1, inits = myinits,
                n.iter=nIter, n.burnin = burnInSteps,
                n.thin=1, DIC=T)

df_latent_mix <- data.frame(z = samples_post$BUGSoutput$sims.list$z)

# grab subject numbers and add to data frame
colnames(df_latent_mix)[which(names(df_latent_mix)=="z.1"):which(names(df_latent_mix)=="z.29")] <- as.character(unique(d_voc$Sub.Num))

# melt data frame
df_melt <- reshape::melt.data.frame(df_latent_mix[,2:length(df_latent_mix)], variable.name = "Sub.Num", value.name = "group_membership")

# change factor label
df_melt %<>% mutate(group_membership_factor = factor(df_melt$value, 
                                                     labels = c("G", "K")),
                    model = "latent_mix") 
```

```{r plot posterior on guessing}
## summarise
ms <- df_melt %>% 
  group_by(variable) %>% 
  summarise(prop_guessing = (length(value) - sum(value)) / length(value)) %>% 
  mutate(prop_guessing_convert = prop_guessing * .1,
         subid = as.character(variable))

ggplot(data=ms, aes(x=reorder(subid, prop_guessing), y = prop_guessing)) +
  geom_bar(stat="identity") +
  guides(fill=F) +
  langcog::scale_fill_solarized() +
  ylim(0,1) +
  xlab('Participant ID#') +
  ylab("Posterior Prob. Guessing") +
  ggtitle("Output of Latent Mixture (\"Guessing\") Model") +
  theme(axis.text.x = element_text(angle=90, vjust = 1))
```
