---
title: "SOL BDA Linear Regression Models"
author: "Kyle MacDonald"
output: html_document
---

In this document, you will find the details of our Bayesian linear regression models for the paper, "Real-time Language Comprehension in American Sign Language."

## Load packages, data, and helper functions

```{r, echo = F}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = F, warning=F, message=F, 
                      results = "hide")

source("../../helper_functions/useful.R")

library(langcog); library(knitr); 
library(rethinking); library(polspline); 
library(magrittr); library(tidyverse)
library(cowplot)

theme_set(theme_classic())
```

```{r paths, echo = F}
data_path <- "../../../data/processed_data/summary_tables/"
sims_path <- "simulations/"
```

```{r, load raw data and mcmc chains}
# raw data
d <- read.csv(paste0(data_path, "sol_ss_dage_models.csv"), stringsAsFactors = F)
d_voc <- read.csv(paste0(data_path, "sol_ss_dvoc_models.csv"), stringsAsFactors = F)

# mcmc chains
df_acc_age <- read.csv(paste0(sims_path, "sol_acc_age_mcmc.csv"), stringsAsFactors = F)
df_acc_voc <- read.csv(paste0(sims_path, "sol_acc_voc_mcmc.csv"), stringsAsFactors = F)
df_rt_age <- read.csv(paste0(sims_path, "sol_rt_age_mcmc.csv"), stringsAsFactors = F)
df_rt_voc <- read.csv(paste0(sims_path, "sol_rt_voc_mcmc.csv"), stringsAsFactors = F)
df_rt_acc <- read.csv(paste0(sims_path, "sol_rt_acc_mcmc.csv"), stringsAsFactors = F)
```

Subset data to get final analysis window for mcmc chains and for data for plotting. Analysis window is based on selecting the middle 90% of the empirical RT distribution.

```{r subset data}
window_final <- "600_2500"
df_acc_age_final <- filter(df_acc_age, window == window_final, slope_prior == 1)
df_acc_voc_final <- filter(df_acc_voc, window == window_final, slope_prior == 1)
df_rt_age_final <- filter(df_rt_age, window == window_final, slope_prior == 1)
df_rt_voc_final <- filter(df_rt_voc, window == window_final, slope_prior == 1)
d_final <- filter(d, window == window_final)
d_voc_final <- filter(d_voc, window == window_final)
```

## Note about priors

We set the standard deviation on the Gaussian prior for the slope parameter using estimated
gains in accuracy and RT between 18-24 months in Fernald et al., (2008).

* RT estimate: is -40ms change with each month of development
* Acc estimate is .0167 change with each month of development

First, we take samples from the prior predictive distribution to show that we are considering 
a plausible set of paraemter values for the slope and interecept. Here we are using our prior knowledge from past work with spoken language showing that expected change in accuracy for each month of age is ~.0167, or 1.6% points. 

Now we can plot the prior distribution of the slope parameter (beta1) on the measurement scale (mean accuracy scores). 

```{r}
prior_slopes_accuracy <- ggplot(aes(beta1_prior), 
                                data = filter(df_acc_age_final, slope_prior == 1)) + 
  geom_histogram(fill = "blue", alpha = 0.7) +
  xlab("Beta1") +
  ylab("Density") +
  geom_vline(xintercept = .016, 
             lty = "solid", color = "red") +
  ggtitle("Prior Predictive on slope for Accuracy")

prior_slopes_rt <- ggplot(aes(beta1_prior), 
                          data = filter(df_rt_age_final, slope_prior == 1)) + 
  geom_histogram(fill = "blue", alpha = 0.7) +
  xlab("Beta0") +
  ylab("Density") + 
  geom_vline(xintercept = -40, 
             lty = "solid", color = "red") +
  ggtitle("Prior Predictive on slope for RT")

gridExtra::grid.arrange(prior_slopes_accuracy, prior_slopes_rt, ncol = 2)
```

On the left panel, we see that the prior puts most of the density on a value of 0, or a null association between age and accuracy. It is truncated at zero to eoncode our directional hypothesis: that the slope parameter should be positive. And the prior does not consider extreme slope values beyond .04, or a 4% gain in accuracy with each month. 

On the right panel, we see that the model makes reasonable predictions for the slope parameter for RT. The distribution is centered around zero, conservatively predicting no association between age and RT. The value from prior data of -40 ms is considered plausible, and extends to extreme values of triple that value.

Now that we are confident that our prior distribution produces reasonable hypotheses, we can quantify the association between children's age/vocab and accuracy/RT on the VLP task. 

## Univariate models

### Accuracy and Age

The first question we ask is whether there is evidence of a linear relationship to measure. We answer this
question by using the Savage-Dickey method for estimating the Bayes Factor. This method uses the statistical fact that the Bayes factor is the ratio of the prior and posterior at the point in the parameter space that reduces the full model to the nested model.

Here we plot the prior and posterior distributions of the slope parameter.

```{r}
ggplot(data=df_acc_age_final) +
  geom_density(aes(x=zbeta1), linetype='dashed') +
  geom_density(aes(x=zbeta1_prior), data = df_acc_age_final) +
  xlim(0, 2) +
  xlab("Standardized Beta")
```

Thus, we treat the null model of no association between age and accuracy as a special case of the linear model where the slope parameter equals 0. We get the Bayes Factor using the Savage-Dickey moethod as described in @wagenmakers2010bayesian, which takes the ratio of the density of the posterior and prior when the slope parameter is zero. 

```{r}
bf <- compute_bf(df_acc_age_final, prior_column_name = "zbeta1_prior", 
                 posterior_column_name = "zbeta1", bound = "lower")
bf_final <- bf
```

The prior and posterior are shown, and the posterior mass at the critical point beta = 0 is lower for the posterior distrubtion. The BF is ~10, meaning that the linear model is 10 times more likely than the null, intercept-only model. Now that we know there is evidence of a linear association, we can summarize the strength of the association and the uncertainty around plausible values for slope parameter.

```{r}
post_mode_b1_acc_age <- round(mean(df_acc_age_final$beta1), 3)
post_mode_b0_acc_age <- round(mean(df_acc_age_final$beta0), 3)
HDI_b1_acc_age <- HDIofMCMC(df_acc_age_final$beta1 , credMass = 0.95 )

## simulate posterior distribution of mu for each value of age to get HDI for MAP regression line
mu.link <- function(x) {df_acc_age_final$beta0 + df_acc_age_final$beta1*x}
age.seq <- seq(from = min(d_final$age_peek_months), to = max(d_final$age_peek_months), by = 1)
mu.acc.age <- sapply(age.seq, mu.link)
mu.mean.acc.age <- apply(mu.acc.age, 2, mean)
mu.HPDI.acc.age <- apply(mu.acc.age, 2, HPDI, prob = 0.95)
mu.HPDI_tidy.acc.age <- data.frame(age_peek_months = age.seq, 
                           hpdi_lower = mu.HPDI.acc.age[1,], hpdi_upper = mu.HPDI.acc.age[2,],
                           mu.mean = mu.mean.acc.age)
```

```{r}
acc_age_plot <- ggplot(data = d_final, aes(x = age_peek_months, y = mean_prop_looking_TD)) +
  geom_point(aes(shape = hearing_status_participant), color = "black", size = 3) +
  geom_point(aes(shape = hearing_status_participant), color = "grey", size = 2) +
  geom_line(aes(x = age_peek_months, y = mu.mean), data = mu.HPDI_tidy.acc.age, size = 1) +
  geom_ribbon(inherit.aes = F, aes(x = age_peek_months, ymin = hpdi_lower, ymax = hpdi_upper), 
              data = mu.HPDI_tidy.acc.age,
              alpha = 0.1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgrey") +
  labs(y = "Mean Accuracy", x = "Child's Age (months)", shape = "Hearing Status: ") +
  coord_cartesian(xlim=c(10, 60), ylim=c(0.2, 1)) +
  scale_x_continuous(breaks = seq(20,50, by = 10)) +
  ggtitle(bquote(list(beta==.(as.character(round(post_mode_b1_acc_age, 3))),
                      HDI=.(paste("95% HDI [", round(HDI_b1_acc_age[1],3) , "," , 
                                  round(HDI_b1_acc_age[2], 3), "]"))))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))
```

### Accuracy and Vocab

Plot prior with posterior on slope parameter.

```{r}
ggplot(data=df_acc_voc_final) +
  geom_density(aes(x=zbeta1), linetype='dashed') +
  geom_density(aes(x=zbeta1_prior), data = df_acc_voc_final) +
  xlim(0,2) +
  xlab("Standardized Beta")
```

We get the Bayes Factor by taking the ratio of the density of the posterior and prior when the slope parameter is zero. 

```{r}
bf <- compute_bf(df_acc_voc_final, prior_column_name = "zbeta1_prior", 
                 posterior_column_name = "zbeta1", bound = "lower")
bf_final <- c(bf_final, bf)
```

Now that we know there is evidence of a linear association, we can summarize the strength of the
association and the uncertainty around plausible values for slope parameter.

```{r}
## get MAP and HDI on slope and intercept
post_mode_b1_accvoc <- round(mean(df_acc_voc_final$beta1), 3)
post_mode_b0_accvoc <- round(mean(df_acc_voc_final$beta0), 3)
HDI_b1_accvoc <- HDIofMCMC(df_acc_voc_final$beta1 , credMass = 0.95 )

## simulate to get HDI for regression line
vocab.seq <- seq(from = min(d_voc$signs_produced), to = max(d_voc$signs_produced), by = 1)
mu.link <- function(x) {df_acc_voc_final$beta0 + df_acc_voc_final$beta1*x}
mu.acc.voc <- sapply(vocab.seq, mu.link)
mu.mean.acc.voc <- apply(mu.acc.voc, 2, mean)
mu.HPDI.acc.voc <- apply(mu.acc.voc, 2, HPDI, prob = 0.95)
mu.HPDI_tidy.acc.voc <- data.frame(signs_produced = vocab.seq, 
                                   hpdi_lower = mu.HPDI.acc.voc[1,], 
                                   hpdi_upper = mu.HPDI.acc.voc[2,],
                                   mu.mean = mu.mean.acc.voc)
```

```{r}
acc_voc_plot <- ggplot(data = d_voc_final, aes(x = signs_produced, y = mean_prop_looking_TD, 
                                    shape = hearing_status_participant)) +
  geom_point(aes(shape = hearing_status_participant), color = "black", size = 3) +
  geom_point(aes(shape = hearing_status_participant), color = "grey", size = 2) +
  geom_line(inherit.aes = F, aes(x = signs_produced, y = mu.mean), 
            data = mu.HPDI_tidy.acc.voc, size = 1) +
  geom_ribbon(inherit.aes = F, aes(x = signs_produced, ymin = hpdi_lower, ymax = hpdi_upper), 
              data = mu.HPDI_tidy.acc.voc,alpha = 0.1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgrey") +
  labs(y = "Mean Accuracy", x = "Reported Signs Produced") +
  guides(shape = F) +
  coord_cartesian(xlim=c(10, 90), ylim=c(0.2, 1)) +
  ggtitle(bquote(list(beta==.(as.character(round(post_mode_b1_accvoc, 3))),
                      HDI=.(paste("95% HDI [", round(HDI_b1_accvoc[1],3) , "," , 
                                  round(HDI_b1_accvoc[2], 3), "]"))))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))
```

### RT and Age

Plot prior with posterior.

```{r}
ggplot(data=df_rt_age_final) +
  geom_density(aes(x=zbeta1), linetype='dashed') +
  geom_density(aes(x=zbeta1_prior), data = df_rt_age_final) +
  xlim(-1, 0) +
  xlab("Standardized Beta")
```

Get Bayes Factor using Savage-Dickey method.

```{r}
bf <- compute_bf(df_rt_age_final, prior_column_name = "zbeta1_prior", 
                 posterior_column_name = "zbeta1", bound = "upper")
bf_final <- c(bf_final, bf)
```

Plot model with data.

```{r}
HDI_rt_age_b1 <- HDIofMCMC(df_rt_age_final$beta1 , credMass = 0.95 )
post_rt_age_mode_b1 <- round(mean(df_rt_age_final$beta1), 3)
post_rt_age_mode_b0 <- round(mean(df_rt_age_final$beta0), 3)

# simulate to get HDI around MAP regression line
mu.link <- function(x) {df_rt_age_final$beta0 + df_rt_age_final$beta1*x}
age.seq <- seq(from = min(d_final$age_peek_months), to = max(d_final$age_peek_months), by = 1)
mu <- sapply(age.seq, mu.link)
mu.mean.rt.age <- apply(mu, 2, mean)
mu.HPDI.rt.age <- apply(mu, 2, HPDI, prob = 0.95)
mu.HPDI_tidy.rt.age <- data.frame(age_peek_months = age.seq, 
                           hpdi_lower = round(mu.HPDI.rt.age[1,], 2), 
                           hpdi_upper = round(mu.HPDI.rt.age[2,], 2),
                           mu.mean = mu.mean.rt.age)
```

```{r}
rt_age_plot <- ggplot(data = d_final, aes(x = age_peek_months, y = median_rt)) +
  geom_point(aes(shape = hearing_status_participant), color = "black", size = 3) +
  geom_point(aes(shape = hearing_status_participant), color = "grey", size = 2) +
  geom_line(inherit.aes = F, aes(x = age_peek_months, y = mu.mean), 
            data = mu.HPDI_tidy.rt.age, size = 1) +
  geom_ribbon(inherit.aes = F, aes(x = age_peek_months, ymin = hpdi_lower, ymax = hpdi_upper), 
              data = mu.HPDI_tidy.rt.age, alpha = 0.1) +
  labs(y = "Mean RT (ms)", x = "Child's Age (months)") +
  guides(shape = F) +
  coord_cartesian(xlim=c(10, 60),  ylim=c(500, 2000)) +
  scale_x_continuous(breaks = seq(20,50, by = 10)) +
  ggtitle(bquote(list(beta==.(as.character(round(post_rt_age_mode_b1, 2))),
                      HDI=.(paste("95% HDI [", round(HDI_rt_age_b1[1],2) , "," , 
                                  round(HDI_rt_age_b1[2], 2), "]"))))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))
```

### RT and Vocab

Plot prior with posterior.

```{r}
ggplot(data=df_rt_voc_final) +
  geom_density(aes(x=beta1), linetype='dashed') +
  geom_density(aes(x=beta1_prior), data = df_rt_voc_final) +
  xlim(-20, 0) +
  xlab("RT Beta")
```

Get Bayes Factor.

```{r}
bf <- compute_bf(df_rt_voc_final, prior_column_name = "zbeta1_prior", 
                 posterior_column_name = "zbeta1", bound = "upper")
bf_final <- c(bf_final, bf)
```

Plot the model with the data.

```{r}
HDI_rt_voc_b1 <- HDIofMCMC( df_rt_voc_final$beta1 , credMass = 0.95 )
post_mode_b1_rt_voc <- round(mean(df_rt_voc_final$beta1), 3)
post_mode_b0_rt_voc <- round(mean(df_rt_voc_final$beta0), 3)

vocab.seq <- seq(from = min(d_voc$signs_produced), to = max(d_voc$signs_produced), by = 1)
mu.link <- function(x) {df_rt_voc_final$beta0 + df_rt_voc_final$beta1*x}
mu <- sapply(vocab.seq, mu.link)
mu.mean.rt.voc <- apply(mu, 2, mean)
mu.HPDI.rt.voc <- apply(mu, 2, HPDI, prob = 0.95)
mu.HPDI_tidy.rt.voc <- data.frame(signs_produced = vocab.seq, 
                           hpdi_lower = mu.HPDI.rt.voc[1,], 
                           hpdi_upper = mu.HPDI.rt.voc[2,], 
                           mu.mean = mu.mean.rt.voc)
```

```{r}
rt_voc_plot <- ggplot(data = d_voc_final, aes(x = signs_produced, y = median_rt)) +
  geom_point(aes(shape = hearing_status_participant), color = "black", size = 3) +
  geom_point(aes(shape = hearing_status_participant), color = "grey", size = 2) +
  geom_line(inherit.aes = F, aes(x = signs_produced, y = mu.mean), 
            data = mu.HPDI_tidy.rt.voc, size = 1) +
  geom_ribbon(inherit.aes = F, aes(x = signs_produced, ymin = hpdi_lower, ymax = hpdi_upper), 
              data = mu.HPDI_tidy.rt.voc, alpha = 0.1) +
  guides(shape = F) +
  labs(y = "Mean RT (ms)", x = "Reported Signs Produced") +
  coord_cartesian(xlim=c(10, 90), ylim=c(500, 2000)) +
  ggtitle(bquote(list(beta==.(as.character(round(post_mode_b1_rt_voc, 2))),
                      HDI=.(paste("95% HDI [", round(HDI_rt_voc_b1[1],2) , "," , 
                                  round(HDI_rt_voc_b1[2], 2), "]"))))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5))
```

### Make final plot

```{r}
# get legend 
legend <- get_legend(acc_age_plot)
# remove legend from acc-age scatter plot
acc_age_plot <- acc_age_plot + theme(legend.position = "none")

# create grid
scat_grid <- plot_grid(acc_age_plot, acc_voc_plot, rt_age_plot, rt_voc_plot, 
                       labels = c("A" , "", "B", ""), align = "v")

# plot grid with shared legend
final_plot <- plot_grid(scat_grid, legend, rel_widths = c(5, .7))

# save plot
save_plot("../../../paper/sol-figs/fig4_scatters.png", final_plot,
          nrow = 2, ncol = 2)
```

### Table of model summaries

```{r}
models <- c("Acc ~ Age", "Acc ~ Voc", "RT ~ Age", "RT ~ Voc")
bfs_final <- bf_final
mean_beta <- c(post_mode_b1_acc_age, post_mode_b1_accvoc, post_rt_age_mode_b1, post_mode_b1_rt_voc)
hdi_lower <- c(HDI_b1_acc_age[1], HDI_b1_accvoc[1], HDI_rt_age_b1[1], HDI_rt_voc_b1[1])
hdi_upper <- c(HDI_b1_acc_age[2], HDI_b1_accvoc[2], HDI_rt_age_b1[2], HDI_rt_voc_b1[2])

# wrap in a table
table1 <- data.frame(models, bfs_final, mean_beta, hdi_lower, hdi_upper)
knitr::kable(table1, digits = 3)
```
