---
title: "SOL BDA Window Selection Analysis"
author: "Kyle MacDonald"
date: "May 3, 2016"
output: html_document
---

In this document you will find the details of a "Window Selection Sensitivity Analysis." 

# Load packages, data, and helper functions

```{r, echo = F}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T, warning=F, message=F, 
                      results = "hide")

source("../../helper_functions/useful.R")

library(langcog); library(knitr); 
library(polspline); library(rethinking); 
library(tidyverse); library(magrittr); 
theme_set(theme_classic())
```

```{r paths, echo = F}
data_path <- "../../../data/processed_data/summary_tables/"
sims_path <- "simulations/"
```

```{r, load raw data and mcmc chains}
# raw data
d <- read.csv(paste0(data_path, "sol_ss_dage_models.csv"), stringsAsFactors = F)
d_voc <- read.csv(paste0(data_path, "sol_ss_dvoc_models.csv"), stringsAsFactors = F)

# mcmc chains
df_acc_age <- read.csv(paste0(sims_path, "sol_acc_age_mcmc.csv"), stringsAsFactors = F)
df_acc_voc <- read.csv(paste0(sims_path, "sol_acc_voc_mcmc.csv"), stringsAsFactors = F)
df_rt_age <- read.csv(paste0(sims_path, "sol_rt_age_mcmc.csv"), stringsAsFactors = F)
df_rt_voc <- read.csv(paste0(sims_path, "sol_rt_voc_mcmc.csv"), stringsAsFactors = F)
```

# Bayes Factor across analysis windows

```{r}
# accuracy and age 
bfs <- plyr::ddply(df_acc_age, c("window", "slope_prior"), compute_bf, prior_column_name = "zbeta1_prior", posterior_column_name = "zbeta1", bound = "lower")
bfs %<>% rename(Acc.Age_BF = V1)
bf_final <- bfs
bf_final

# accuracy and vocabulary 
bfs <- plyr::ddply(df_acc_voc, c("window", "slope_prior"), compute_bf, prior_column_name = "zbeta1_prior", posterior_column_name = "zbeta1", bound = "lower")
bfs %<>% rename(Acc.Voc_BF = V1)
bf_final <- bind_cols(bf_final, select(bfs, Acc.Voc_BF))
bf_final

# rt and age
bfs <- plyr::ddply(df_rt_age, c("window", "slope_prior"), compute_bf, prior_column_name = "zbeta1_prior", posterior_column_name = "zbeta1", bound = "upper")
bfs %<>% rename(RT.Age_BF = V1)
bf_final <- bind_cols(bf_final, select(bfs, RT.Age_BF))
bf_final

# rt and vocabulary
bfs <- plyr::ddply(df_rt_voc, c("window", "slope_prior"), compute_bf, prior_column_name = "zbeta1_prior", posterior_column_name = "zbeta1", bound = "upper")
bfs %<>% rename(RT.Voc_BF = V1)
bf_final <- bind_cols(bf_final, select(bfs, RT.Voc_BF))
bf_final
```

# Parameter estimates across analysis windows and priors

```{r}
# accuracy and age
ms_windows_acc <- df_acc_age %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            mode = find_mode(beta1),
            lower_95_HDI = HDIofMCMC(beta1)[1],
            upper_95_HDI = HDIofMCMC(beta1)[2]) %>% 
  mutate(model = "Accuracy~Age")

# accuracy and vocabulary
ms_windows_acc <- df_acc_voc %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            mode = find_mode(beta1),
            lower_95_HDI = HDIofMCMC(beta1)[1],
            upper_95_HDI = HDIofMCMC(beta1)[2]) %>% 
  mutate(model = "Accuracy~Vocab") %>% 
  bind_rows(ms_windows_acc, .)

# rt and age
ms_windows_rt <- df_rt_age %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            mode = find_mode(beta1),
            lower_95_HDI = HDIofMCMC(beta1)[1],
            upper_95_HDI = HDIofMCMC(beta1)[2]) %>% 
  mutate(model = "RT~Age") 

# rt and vocabulary
ms_windows_rt <- df_rt_voc %>% 
  group_by(window, slope_prior) %>% 
  summarise(mean = mean(beta1),
            mode = find_mode(beta1),
            lower_95_HDI = HDIofMCMC(beta1)[1],
            upper_95_HDI = HDIofMCMC(beta1)[2]) %>% 
  mutate(model = "RT~Vocab") %>% 
  bind_rows(ms_windows_rt, .)
```

# Window Sensitivity Plot

Here we show that our parameter estimates for the association between age/vocabulary and accuracy/RT are robust to different choices of analysis windows. We fit each model to a different analysis window +/- 300 ms from the final analysis window. Recall that the final analysis window was selected based on the empirical distribution of RTs in the VLP task: that is, we selected the middle 90% of the distrbution since these responses are most likely to be meaningful responses. 

This plot shows the different slope coefficients with their 95% HDI intervals for both accuracy models for each time window. 

```{r}
acc_coefplot <- ggplot(aes(x = as.factor(slope_prior), y = mean, color = window), 
                       data = ms_windows_acc) +
  geom_pointrange(aes(ymin = lower_95_HDI, ymax = upper_95_HDI), 
                  position = position_jitter(width = 0.4),
                  alpha = 0.7, size = 0.8) +
  geom_hline(yintercept = 0, lty = "dashed") +
  coord_flip() +
  facet_grid(model~.) +
  ylim(-.015, .015) +
  xlab("SD of Prior") +
  ylab("Accuracy Slope") +
  ggtitle("Accuracy Models") +
  theme_bw() +
  theme(plot.title = element_text(size = 18),
        axis.title.x = element_text(colour="grey30",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey30",size=22,
                                    hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        strip.text.x = element_text(size = 16),
        panel.grid.major=element_blank(),
        panel.spacing = unit(2, "lines")) +
  guides(color = F) 
  

rt_coefplot <- ggplot(aes(x = as.factor(slope_prior), y = mean, color = window), 
                      data = ms_windows_rt) +
  geom_pointrange(aes(ymin = lower_95_HDI, ymax = upper_95_HDI), 
                  position = position_jitter(width = 0.4),
                  alpha = 0.7, size = 0.8) +
  geom_hline(yintercept = 0, lty = "dashed") +
  coord_flip() +
  facet_grid(model~.) +
  ylim(-30, 30) +
  xlab(NULL) +
  ylab("RT Slope") +
  ggtitle("RT Models") +
  theme_bw() +
  theme(plot.title = element_text(size = 18),
        axis.title.x = element_text(colour="grey30",size=22,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey30",size=22,
                                    hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=18,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        strip.text.x = element_text(size = 16),
        panel.grid.major=element_blank(),
        panel.spacing = unit(2, "lines"),
        legend.justification=c(1,1), legend.position=c(1,1)) 

gridExtra::grid.arrange(acc_coefplot, rt_coefplot, ncol =2)
```

### Plot the prior of the slope parameter for accuracy and RT slopes. 

Convert prior on slope parameter from precision to standard deviation. 

* precision = $1/stdev^2$

```{r}
df_acc_age %<>%
  mutate(slope_prior_stdev = round(sqrt((1/slope_prior)), 1))

df_rt_age %<>%
  mutate(slope_prior_stdev = round(sqrt((1/slope_prior)), 1))
```


```{r}
a <- ggplot(aes(x=beta1_prior), data = df_acc_age) +
  geom_density(size = 1) +
  facet_wrap(~slope_prior_stdev, ncol = 1) +
  geom_vline(xintercept = 0.0167, color = "blue", size = 1) +
  xlab("Slope Value (Acc)") +
  ylab("Density") +
  xlim(0, .075) +
  ggtitle("Accuracy Model") +
  theme(axis.title.x = element_text(colour="grey30",size=12,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey30",size=12,
                                    hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        panel.grid.major=element_blank(),
        panel.spacing = unit(2, "lines"))

b <- ggplot(aes(x=beta1_prior), data = df_rt_age) +
  geom_density(size = 1) +
  facet_wrap(~slope_prior_stdev, ncol = 1) +
  geom_vline(xintercept = -30, color = "blue", size = 1) +
  xlab("Slope Value (RT)") +
  ylab(NULL) +
  xlim(0, -90) +
  ggtitle("RT Model") +
  theme(axis.title.x = element_text(colour="grey30",size=12,
                                    angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.title.y = element_text(colour="grey30",size=12,
                                    hjust=0.5,vjust=0.5,face="plain"),
        axis.text.x = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        axis.text.y = element_text(colour="grey20",size=12,
                                   angle=0,hjust=0.5,vjust=0,face="plain"),
        panel.grid.major=element_blank(),
        panel.spacing = unit(2, "lines"))

gridExtra::grid.arrange(a, b, ncol = 2)
```

Latex table of BFs.

```{r}
bf_final %<>%
  mutate(slope_prior_stdev = round(sqrt((1/slope_prior)), 1)) %>% 
  rename(Window = window, SD_Slope = slope_prior_stdev, Acc_Age = Acc.Age_BF,
         Acc_Vocab = Acc.Voc_BF, RT_Age = RT.Age_BF, RT_Vocab = RT.Voc_BF)
```

```{r}
table_final <- xtable::xtable(select(bf_final, Window, SD_Slope, Acc_Age, Acc_Vocab, RT_Age, RT_Vocab), digits = 1, align = c("lc|rrrrr"),
                              caption = "Bayes Factors for all four linear models fit to three different analysis windows using four different parameterizations of the prior distribution for the slope parameter.")

xtable::print.xtable(table_final, include.rownames =F)
```