---
title: "SOL BDA Categorical Models"
author: "Kyle MacDonald"
output: html_document
bibliography: bda.bib
---

In this document, you will find the details of our Bayesian categorical models for the paper, "Real-time Language Comprehension in American Sign Language." 

## Load packages and data

```{r, echo = F}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T,warning=F, message=F, results = "hide")

source("../../helper_functions/useful.R")

library(langcog); library(knitr); library(forcats);
library(polspline); library(rethinking); 
library(magrittr); library(tidyverse)
theme_set(ggthemes::theme_few())
```

Load data

```{r}
d <- read_csv("../../../data/processed_data/summary_tables/sol_ss_all_600_2500.csv")
```

Set seed to reproduce exact simulation values.

```{r}
set.seed(123)
```


## Age as categorical variable

All categorical models were fit using STAN [@rstan], and are based on code adapted from @mcelreath2016statistical.  

First we need to create dummy variables for the relevant group comparisons.

```{r dummy vars}
d_model <- d %>% 
  filter(value_cat == "Target") %>% 
  select(Sub.Num, age_group_collapsed, hearing_status_participant, 
         mean_prop_looking_TD, median_ct_rt) %>% 
  rename(median_rt = median_ct_rt,
         age_group_string = age_group_collapsed) %>% 
  mutate(age_group = ifelse(age_group_string == "Adults", 1, 0),
         hearing_group = ifelse(hearing_status_participant == "hearing", 1, 0),
         logit_acc = car::logit(mean_prop_looking_TD)) 
```

### CODA vs. Deaf

Compare accuracy for deaf and hearing kids. All priors are vague since we are just concerned with parameter estimation. 

```{r hearing_status acc}
acc_hearing_stat_cat_targ.m <- map2stan(
  alist(
    logit_acc ~ dnorm(mu, sigma),
    mu <- Intercept + b_Hearing*hearing_group,
    Intercept ~ dnorm(0, 10), 
    b_Hearing ~ dnorm(0, 1),
    sigma ~ dunif(0, 10)
  ),
  data = data.frame(select(filter(d_model, age_group_string == "Kids"),
                logit_acc, hearing_group)))

# get samples
post_hearing_stat.acc <- extract.samples(acc_hearing_stat_cat_targ.m)
hearing <- post_hearing_stat.acc$Intercept
deaf <- post_hearing_stat.acc$b_Hearing + post_hearing_stat.acc$Intercept

post_df_hearing_stat.acc <- data.frame(hearing, deaf) %>% 
  gather(key = hearing_status, value = posterior_sample) %>% 
  mutate(age_group = "kids",
         measure = "accuracy",
         prob_acc_sample = logit2prob(posterior_sample))


post_df_hearing_stat.acc %>% 
  group_by(hearing_status) %>% 
  summarise(m = round(mean(prob_acc_sample), 2))

# test contrast
diff.deaf.hearing <- logit2prob(hearing) - logit2prob(deaf)
round(quantile(diff.deaf.hearing, probs = c(0.025, 0.5, 0.975)), 2)
```

Compare RT for deaf and hearing kids.

```{r hearing_status rt}
rt_hearing_stat.m <- map2stan(
  alist(
    median_rt ~ dnorm(mu, sigma),
    mu <- Intercept + b_Hearing*hearing_group,
    Intercept ~ dnorm(1300, 100), 
    b_Hearing ~ dnorm(0, 500),
    sigma ~ dunif(0, 500)
  ),
  data = data.frame(select(filter(d_model, age_group_string == "Kids"), 
                median_rt, hearing_group))
)

# extract samples
post_hearing_stat.rt <- extract.samples(rt_hearing_stat.m)
hearing <- as.numeric(post_hearing_stat.rt$Intercept)
deaf <- as.numeric(post_hearing_stat.rt$b_Hearing + post_hearing_stat.rt$Intercept)

post_df_hearing_stat.rt <- data.frame(hearing, deaf) %>% 
  gather(key = hearing_status, value = posterior_sample) %>% 
  mutate(age_group = "kids",
         measure = "rt")

post_df_hearing_stat.rt %>% 
  group_by(hearing_status) %>% 
  summarise(m = round(mean(posterior_sample), 2))

# test contrast
diff.deaf.hearing.rt <- hearing - deaf
round(quantile(diff.deaf.hearing.rt, probs = c(0.025, 0.5, 0.975)), 2)
```

### Accuracy and RT for kids compared to adults

Accuracy comparison

```{r age_groups_adults acc}
acc_age_cat_targ.m.collapsed <- map2stan(
  alist(
    logit_acc ~ dnorm(mu, sigma),
    mu <- Intercept + b_Adults*age_group,
    Intercept ~ dnorm(0, 10), 
    b_Adults ~ dnorm(0, 1),
    sigma ~ dunif(0, 10)
  ),
  data = data.frame(select(d_model, logit_acc, age_group))
)

post_ages.acc_collapsed <- extract.samples(acc_age_cat_targ.m.collapsed)

kids <- post_ages.acc_collapsed$Intercept
adults <- post_ages.acc_collapsed$b_Adults + post_ages.acc_collapsed$Intercept

# get samples
post_df.acc.collapsed <- data.frame(kids, adults) %>% 
  gather(key = age_group, value = posterior_sample) %>% 
  mutate(hearing_status = "deaf", 
         measure = "accuracy",
         prob_acc_sample = logit2prob(posterior_sample))

# summarize
post_df.acc.collapsed %>% 
  group_by(age_group) %>% 
  summarise(m = round(mean(prob_acc_sample), 2))

diff.acc.kids.adults <- logit2prob(adults) - logit2prob(kids)
round(quantile(diff.acc.kids.adults, probs = c(0.025, 0.5, 0.975)), 2)
```

RT comparison

```{r age_group_adults rt}
rt_age_cat_collapsed.m <- map2stan(
  alist(
    median_rt ~ dnorm(mu, sigma),
    mu <- Intercept + b_Adults*age_group,
    Intercept ~ dnorm(1300, 100), 
    b_Adults ~ dnorm(0, 500),
    sigma ~ dunif(0, 500)
  ),
  data = data.frame(select(d_model, median_rt, age_group))
)

post_ages.rt_collapsed <- extract.samples(rt_age_cat_collapsed.m)

kids <- as.numeric(post_ages.rt_collapsed$Intercept)
adults <- as.numeric(post_ages.rt_collapsed$b_Adults + post_ages.rt_collapsed$Intercept)

post_df.rt.collapsed <- data.frame(kids, adults) %>% 
  gather(key = age_group, value = posterior_sample) %>% 
  mutate(hearing_status = "deaf", 
         measure = "rt")

post_df.rt.collapsed %>% 
  group_by(age_group) %>% 
  summarise(m = round(mean(posterior_sample), 2))


diff.old.young.rt.collapsed <- adults - kids
round(quantile(diff.old.young.rt.collapsed, probs = c(0.025, 0.5, 0.975)), 2)
```

### Merge model output for ACC/RT coda-deaf comparisons to be used in the plotting script.

```{r}
model_output <- bind_rows(post_df_hearing_stat.acc, post_df_hearing_stat.rt,
                          post_df.acc.collapsed, post_df.rt.collapsed)

write_csv(model_output, "simulations/group_means_acc_rt.csv")
```

## References