---
title: "SOL item analysis"
author: "Kyle MacDonald"
output: html_document
---

```{r setup, include = F}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T,warning=F, message=F)
```

```{r}
source("../helper_functions/useful.R")
library(langcog); library(knitr); library(forcats)
library(magrittr);library(rethinking); library(BayesFactor)
library(car); library(tidyverse) 
theme_set(theme_classic())
```

Read data:

* Sign lengths
* RT and accuracy for each sign

```{r}
d <- read_csv("../../data/processed_data/summary_tables/sol_trial_level_df.csv")
d.sign_lengths <- read_csv("../../data/demographics/target_sign_lengths_all.csv",
                         col_types = "ccccnnnnn")
```

Split sign variable into carrier and target information

```{r}
d.sign_lengths %<>% separate(sign, into = c("clean_target_img", "carrier"), sep = "_")
```

Separate trial number information and convert the data frame to long format to make merging with VP measures easier.

```{r}
# separate
d.sign_lengths %<>% separate(trial_num_peek, 
                             into = c("Tr.Num.1", "Tr.Num.2", "Tr.Num.3",
                                      "Tr.Num.4"), sep = ",", fill = "right")

# gather 
d.sign_lengths %<>% gather(key = Key, value = Tr.Num, Tr.Num.1:Tr.Num.4)

# remove NAs
d.sign_lengths %<>% filter(is.na(Tr.Num) == F) %>% 
  mutate(Tr.Num = as.integer(Tr.Num)) %>% 
  select(-Key)
```

Create "signer" variable in summary table so we can add the sign length information.

```{r}
d %<>% mutate(signer = ifelse(stimuli == "V1", "p", "r"))
```

Now we can add the sign length information to our data frame and calculate a new variable where we add 200 ms to the length of the target sign in order to account for the time it takes to program an eye movement. That is, we consider eye movements that occurred up to 200 ms after the offset of the target sign as being initiated prior to sign offset, providing evidence for incremental processing. 

```{r}
d %<>% left_join(., d.sign_lengths, by = c("clean_target_img", "signer", "Tr.Num", "stimuli"))

d %<>% filter(is.na(length_ms) == F) %>% mutate(length_ms_200 = length_ms + 200)
```

## Item-level Analysis

Get the difference between RT and sign length for all signs. We also get the proportion of sign needed before shifting in order to normalize for the different sign lengths.

```{r}
d %<>% mutate(shift_diff_offset = (RT - length_ms_200) / 1000,
              prop_sign_to_shift = RT / length_ms_200)
```

Next, we do the same kind of analysis but using the `prop_sign_needed` variable, which should help account for the signs being different lengths. Note that we are only including correct shifts since these are most likely to be driven by speed of lexical acess.

```{r}
ss <-  d %>% 
  filter(correct == 1, RT <= 2500) %>%
  group_by(Sub.Num, clean_target_img, age_code) %>% 
  summarise(m_prop_sign_needed = mean(prop_sign_to_shift)) 

ss.all.signs <- d %>% 
  filter(correct == 1, RT <= 2500) %>%
  group_by(Sub.Num, age_code) %>% 
  summarise(m_prop_sign_needed = mean(prop_sign_to_shift)) 
```

Plot distribution of prop sign needed variable

```{r}
ss.all.signs %>% 
  ggplot(., aes(x = m_prop_sign_needed, color = age_code)) +
  geom_density(adjust = 1.5, size = 1) +
  xlim(0,1.5)
```

Flag outliers +/- 2 sd from the mean for each group

```{r}
ss %<>% 
  filter(is.na(m_prop_sign_needed) == F) %>% 
  group_by(age_code) %>% 
  mutate(m = mean(m_prop_sign_needed),
         stdev = sd(m_prop_sign_needed, na.rm = T),
         outlier = ifelse(m_prop_sign_needed <= m - 2 * stdev |
                            m_prop_sign_needed >= m + 2 * stdev, "yes", "no")) 

ss.all.signs %<>% 
  filter(is.na(m_prop_sign_needed) == F) %>% 
  group_by(age_code) %>% 
  mutate(m = mean(m_prop_sign_needed),
         stdev = sd(m_prop_sign_needed),
         outlier = ifelse(m_prop_sign_needed <= m - 2 * stdev |
                            m_prop_sign_needed >= m + 2 * stdev, "yes", "no"))
```

Get 95% HDI for each sign.

```{r}
samples <- ss %>% 
  #filter(outlier == "no") %>% 
  as.data.frame() %>% 
  lmBF(m_prop_sign_needed ~ clean_target_img + age_code, data = .,
       posterior = TRUE, iterations = 5000) %>% 
  data.frame()

samples.long <- samples %>% 
  gather(key = sign, value = sign_coef, clean_target_img.ball:clean_target_img.teddy) %>% 
  gather(key = age_code, value = age_coef, age_code.adult:age_code.child) %>% 
  mutate(sign = gsub(x = sign, pattern = "clean_target_img.", replacement = ""),
         age_code = gsub(x = age_code, pattern = "age_code.", replacement = ""))

samples.long %<>% mutate(posterior.estimate = mu + age_coef + sign_coef)
```

```{r}
samples.all.signs <- ss.all.signs %>% 
  #filter(outlier == "no") %>% 
  as.data.frame() %>% 
  lmBF(m_prop_sign_needed ~ age_code, data = .,
       posterior = TRUE, iterations = 5000) %>% 
  data.frame()

samples.all.signs.long <- samples.all.signs %>% 
  gather(key = age_code, value = age_coef, age_code.adult:age_code.child) %>% 
  mutate(age_code = gsub(x = age_code, pattern = "age_code.", replacement = ""))

samples.all.signs.long %<>% mutate(posterior.estimate = mu + age_coef)
```

Now summarize

```{r}
ms.all.signs <- samples.all.signs.long %>% 
  group_by(age_code) %>% 
  summarise(mean = mean(posterior.estimate),
            lower = quantile(posterior.estimate, prob = 0.025),
            upper = quantile(posterior.estimate, prob = 0.975)) %>% 
  mutate(sign = "all signs")
```

```{r}
ms <- samples.long %>% 
  group_by(age_code, sign) %>% 
  summarise(mean = mean(posterior.estimate),
            lower = quantile(posterior.estimate, prob = 0.025),
            upper = quantile(posterior.estimate, prob = 0.975)) 
```

```{r}
ms.final <- bind_rows(ms, ms.all.signs) %>% 
  mutate(all_signs = ifelse(sign == "all signs", "yes", "no")) %>% 
  group_by(age_code) %>% 
  do(add_plot_order(.)) %>% 
  ungroup() %>% 
  mutate(age_code = fct_relevel(as.factor(age_code), "child"))
```

Make the plot

```{r}
levels(ms.final$age_code) <- c("children", "adults")

item_plot <- ms.final %>% 
  ggplot(aes(x = reorder(sign, plot_order), y = mean,
         color = all_signs, shape = all_signs, size = all_signs)) +
  scale_color_manual(values = c("black", "red")) +
  scale_shape_manual(values = c(20, 18)) +
  scale_size_manual(values = c(0.8, 1.4)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_pointrange(aes(ymin = lower, ymax = upper)) +
  scale_x_discrete(expand = c(0.1,0)) +
  coord_flip() +
  guides(color = F, shape = F, size = F) +
  scale_y_continuous(limits = c(0.1, 1.6), breaks = c(0.25, 0.5, 0.75, 1.0, 1.25, 1.5)) +
  labs(y = "Proportion of Target Sign Processed Prior to Gaze Shift", x = "Target sign") +
  facet_wrap(~age_code, ncol = 2) +
  ggthemes::theme_few()
```

Save plot

```{r}
ggsave(item_plot, filename = "../../paper/sol-figs/fig3_item_analysis.png", 
       device = "png", width = 7, height = 4)
```

Print summary information about sign lengths

```{r}
d.sign_lengths %>% 
  .$length_ms %>% 
  summary() 
```

## Incremental Bayesian analysis model

Estimate the difference between kids and adults using bayesian estimation.

First we need to create dummy variables for the relevant group comparisons.

```{r dummy vars}
ss.model <- ss.all.signs %>% mutate(age_code_num = ifelse(age_code == "adult", 1, 0))
```

```{r prop_sign_needed}
m1 <- map2stan(
  alist(
    m_prop_sign_needed ~ dnorm(mu, sigma),
    mu <- Intercept + b_kid*age_code_num,
    Intercept ~ dnorm(1.0, 10), 
    b_kid ~ dnorm(0, 1),
    sigma ~ dunif(0, 10)
  ),
  data = data.frame(select(ss.model, m_prop_sign_needed, age_code_num))
)

# get samples
m1.samples <- extract.samples(m1)
adults <- m1.samples$Intercept
kids <- m1.samples$b_kid + m1.samples$Intercept

# create data frame with samples
post_df <- data.frame(adults, kids) %>% 
  gather(key = age_code, value = posterior_sample) %>% 
  mutate(age_code = as.factor(age_code))
```

Test contrast of differences between kids and adults by getting the mean, and 95% HDI on the difference in means.

```{r}
diff.post <- kids - adults

round(quantile(diff.post , probs = c(0.025, 0.5, 0.975)), 2)
```

The HDI does not include zero, indicating that there is evidence for a difference between kids and adults in the prop. sign processed prior to shifting.

-------

Next, we estimate whether each group (kids and adults) are shifting prior to the offset of the target sign.

```{r}
d.kid <- ss.model %>% 
  ungroup() %>% 
  filter(age_code == "child") %>% 
  select(m_prop_sign_needed)

m2.kids <- map2stan(
  alist(
    m_prop_sign_needed ~ dnorm(mu, sigma),
    mu <- Intercept,
    Intercept ~ dnorm(1.0, 10), 
    sigma ~ dunif(0, 10)
  ),
  data = data.frame(d.kid)
)

# get smaples
m2.kids.samples <- extract.samples(m2.kids)
```

```{r}
round(quantile(m2.kids.samples$Intercept , probs = c(0.025, 0.5, 0.975)), 2)
```

Next, we estimate whether each group (kids and adults) are shifting prior to the offset of the target sign.

```{r}
d.adult <- ss.model %>% 
  ungroup() %>% 
  filter(age_code == "adult") %>% 
  select(m_prop_sign_needed)

m2.adult <- map2stan(
  alist(
    m_prop_sign_needed ~ dnorm(mu, sigma),
    mu <- Intercept,
    Intercept ~ dnorm(1.0, 10), 
    sigma ~ dunif(0, 10)
  ),
  data = data.frame(d.adult)
)

# get smaples
m2.adult.samples <- extract.samples(m2.adult)
```

```{r}
round(quantile(m2.adult.samples$Intercept , probs = c(0.025, 0.5, 0.975)), 2)
```

## Incremental frequentist analysis model

One sample t-test comparing prop shifting against null hypothesis: 1.0.

```{r}
ss.all.signs %>% 
  filter(age_code == "child") %>% 
  .$m_prop_sign_needed %>% 
  t.test(mu = 1.0)
```

```{r}
ss.all.signs %>% 
  filter(age_code == "adult") %>% 
  .$m_prop_sign_needed %>% 
  t.test(mu = 1.0)
```
