---
title: "SOL MLE Analysis"
author: "Kyle MacDonald"
output:
  word_document: default
  html_document: default
---

This document contains all of the frequentist analyses that appear in the supplemental online materials for the paper, "Real-time lexical comprehension in young children learning American Sign Language (ASL)."

## Setup 

```{r}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T,warning=F, message=F)
library(langcog); library(knitr); library(forcats); library(lme4)
library(magrittr); library(tidyverse); library(car)

theme_set(ggthemes::theme_few())
```

## Load data

```{r}
d_2500 <- read.csv("../../data/processed_data/summary_tables/sol_ss_all_600_2500.csv")
```

Make a table of background information

```{r}
d_2500 %>% 
  filter(age_group_collapsed == "Kids", include == "yes") %>% 
  select(Sub.Num, age_peek_months, hearing_status_participant, gender) %>% 
  group_by(hearing_status_participant) %>% 
  unique() %>% 
  summarise(n = n(),
            Mean.age  = mean(age_peek_months),
            SD.age = sd(age_peek_months),
            Min.age = min(age_peek_months),
            Max.age = max(age_peek_months)
            ) %>% 
  mutate_if(is.numeric, round, digits = 1) %>% 
  rename(Hearing.status = hearing_status_participant) %>% 
  kable()
```

```{r}
d_2500 %>% 
  filter(age_group_collapsed == "Kids", include == "yes") %>% 
  select(Sub.Num, age_peek_months, hearing_status_participant, gender) %>% 
  unique() %>% 
  summarise(n = n(),
            Mean.age  = mean(age_peek_months),
            SD.age = sd(age_peek_months),
            Min.age = min(age_peek_months),
            Max.age = max(age_peek_months)
            ) %>% 
  mutate_if(is.numeric, round, digits = 1) 
```

## Plot distributions of dependent variables (Acc and RT)

Mean accuracy for each child:

```{r}
acc_dist <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD) %>% 
  unique() %>% 
  ggplot(aes(x = mean_prop_looking_TD)) +
  geom_line(stat="density", size = 1.5, adjust = 1.5) +
  labs(x = "Accuracy") +
  xlim(0, 1)
```

Mean RT for each child: 

```{r}
rt_dist <- d_2500 %>%
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt) %>% 
  unique() %>% 
  ggplot(aes(x = median_ct_rt)) +
  geom_line(stat="density", size = 1.5, adjust = 2) +
  labs(x = "RT (msec)") +
  xlim(500, 2000)
```

Make plot

```{r}
cowplot::plot_grid(acc_dist, rt_dist, labels = c("A", "B"))
```

## Show distribution of hearing status over age

```{r}
ms_hs <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, age_peek_months, hearing_status_participant) %>% 
  unique() %>% 
  group_by(hearing_status_participant) %>% 
  summarise(mean_val = mean(age_peek_months))

d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, age_peek_months, hearing_status_participant) %>% 
  unique() %>% 
  ggplot(aes(x = age_peek_months, color = hearing_status_participant)) +
  geom_line(stat="density", size = 1, adjust = 2) +
  geom_vline(aes(xintercept = mean_val, color = hearing_status_participant), 
             data = ms_hs, size = 1, linetype = "dashed") +
  labs(x = "Age (months)",
       fill = "Hearing Status") +
  xlim(0, 70)  +
  scale_color_manual(values = c("darkorange", "dodgerblue"))  +
  theme(legend.position = "top")
  
```

## Analysis 1: Estimate difference in Acc/RT for hearing/deaf signers

```{r}
d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD, age_peek_months, hearing_status_participant) %>%
  unique() %>% 
  t.test(mean_prop_looking_TD ~ hearing_status_participant, data = .)
```

```{r}
d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt, age_peek_months, hearing_status_participant) %>%
  unique() %>% 
  t.test(median_ct_rt ~ hearing_status_participant, data = .)
```

## Analysis 2: Evidence of incremental processing

For this analysis, see the .Rmd file: "sol-incremental-analysis.Rmd"

## Analysis 3: estimate relations of Acc/RT to age/vocab using MLE 

```{r}
m1 <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD, age_peek_months, hearing_status_participant) %>%
  unique() %>% 
  lm(logit(mean_prop_looking_TD) ~ age_peek_months + hearing_status_participant, data = .)

m1.int <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD, age_peek_months, hearing_status_participant) %>%
  unique() %>% 
  lm(logit(mean_prop_looking_TD) ~ age_peek_months * hearing_status_participant, data = .)

m1.model.comp <- anova(m1, m1.int) # the more complicated model with an interaction term for hearing status does not improve fit

m1 %>% 
  broom::tidy() %>% 
  mutate(one_sided_p =  pt(-abs(statistic), df = 28)) %>% 
  kable(digits = 3)
```

```{r}
m2 <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt, age_peek_months, hearing_status_participant) %>% 
  unique() %>% 
  lm(median_ct_rt ~ age_peek_months + hearing_status_participant, data = .)

m2.int <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt, age_peek_months, hearing_status_participant) %>% 
  unique() %>% 
  lm(median_ct_rt ~ age_peek_months * hearing_status_participant, data = .)

m2.model.comp <- anova(m2, m2.int) # adding interaction term does not help model fit and is not sig, so we can drop

m2 %>% 
  broom::tidy() %>% 
  mutate(one_sided_p =  pt(-abs(statistic), df = 28)) %>% 
  kable(digits = 3)
```

```{r}
m3 <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD, signs_produced, hearing_status_participant) %>% 
  unique() %>% 
  lm(logit(mean_prop_looking_TD) ~ signs_produced + hearing_status_participant, data = .)

m3.int <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, mean_prop_looking_TD, signs_produced, hearing_status_participant) %>% 
  unique() %>% 
  lm(logit(mean_prop_looking_TD) ~ signs_produced * hearing_status_participant, data = .)

m3.model.comp <- anova(m3, m3.int) # adding interaction term does not improve model fit and is not sig

m3 %>% 
  broom::tidy() %>% 
  mutate(one_sided_p =  pt(-abs(statistic), df = 28)) %>% 
  kable(digits = 3)
```

```{r}
m4 <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt,  signs_produced, hearing_status_participant) %>% 
  unique() %>% 
  lm(median_ct_rt ~ signs_produced + hearing_status_participant, data = .)

m4.int <- d_2500 %>% 
  filter(age_group != "Adults", value_cat == "Target") %>% 
  select(Sub.Num, median_ct_rt,  signs_produced, hearing_status_participant) %>% 
  unique() %>% 
  lm(median_ct_rt ~ signs_produced * hearing_status_participant, data = .)

m4.model.comp <- anova(m4, m4.int) # adding interaction term does not improve model fit and is not sig

m4 %>% 
  broom::tidy() %>% 
  mutate(one_sided_p =  pt(-abs(statistic), df = 28)) %>% 
  kable(digits = 3)
```

## Age and vocab correlation

```{r}
d_2500 %>% 
  filter(age_group_collapsed == "Kids", include == "yes") %>% 
  select(Sub.Num, Months, signs_produced) %>% 
  unique() %>% 
  summarise(corr = cor(Months, signs_produced, use='pairwise.complete.obs')) 
```

