---
title: "SOL Reliability Analysis"
author: "Kyle MacDonald"
output: html_document
---

This document contains all of the interal reliability analyses for the processing measures reported in the paper, "Real-time lexical comprehension in young children learning American Sign Language (ASL)."

```{r}
rm(list=ls()) # clear workspcace
knitr::opts_chunk$set(fig.height=4, fig.width=7, cache = T,warning=F, message=F)
library(langcog); library(knitr); library(forcats); library(lme4)
library(magrittr); library(tidyverse); library(car)

theme_set(ggthemes::theme_few())
```

## Split-half reliability analysis

Approach taken from (http://schatz.sju.edu/multivar/reliab/splithalf.html).

Load trial-level data

```{r}
trial_df <- read_csv("../../data/processed_data/summary_tables/sol_trial_level_df.csv")
```

First, we create two bins of trials for each participant by sorting based on even vs. odd trial numbers.

```{r}
trial_df %<>% mutate(split_half = ifelse(Tr.Num %% 2 == 0, "first", "second"))
```

```{r, echo=F}
trial_df %>% 
  group_by(Sub.Num, age_code, split_half) %>% 
  summarise(n_trials = n())
```

```{r}
split_df <- trial_df %>% 
  group_by(Sub.Num, split_half, age_code) %>% 
  summarise(mean_acc = mean(Accuracy, na.rm = T),
            median_rt = median(RT, na.rm = T)) %>%
  gather(key = measure, value = value, mean_acc, median_rt) %>% 
  spread(key = split_half, value = value) 
```

```{r}
labels <- c(mean_acc = "Accuracy", median_rt = "RT")

ggplot(aes(x = first, y = second, color = age_code), data = split_df) +
  geom_smooth(method = "lm", se = F) +
  geom_point() +
  facet_wrap(~measure, scales = "free", labeller = labeller(measure = labels)) +
  scale_color_manual(values = c("darkorange", "dodgerblue")) +
  labs(x = "First Half", y = "Second Half", color = "Age group") 
```

```{r}
## compute pearson r
sp_r <- split_df %>% 
  group_by(measure) %>% 
  do(data.frame(pearson_r = cor(.$first, .$second, method = "pearson")))

## spearman-brown correction
sp_r %>% 
  mutate(sph_rel = round((2 * pearson_r) / (1 + pearson_r), 3)) %>% 
  kable(digits = 3)
```

Use `alpha()` function in the psych package.

```{r}
acc <- split_df %>% filter(measure == "mean_acc") %>% ungroup() %>% select(first, second)
rel_acc <- psych::alpha(acc)

# print cronbach's alpha
round(rel_acc$total$raw_alpha, 2)
```

```{r}
rt <- split_df %>% filter(measure == "median_rt") %>% ungroup() %>% select(first, second)
rel_rt <- psych::alpha(rt)

# print cronbach's alpha
round(rel_rt$total$raw_alpha, 2)
```

