---
title: "Sol-Gating Analysis"
author: "Kyle MacDonald"
date: "April 27, 2015"
output: html_document
---

This script analyzes data for sol-gating experiment. The goal 
of this analysisis to find the precise gate when participants 
can reliably identify the sign for each sign used in the SOL 
stimulus set.

Load libraries.

```{r, echo=F, warning=F, message=FALSE}
rm(list=ls())
source("../helpers/useful.R")
require(magrittr)
```

Read in data.

```{r}
df <- read.csv("sol_gating_processed-df.csv")
```

### Descriptives

```{r}
df %>%
    group_by(id) %>%
    mutate(num_trials = max(trial)) %>%
    select(id, gender, age, asl_fluency, age_learned_asl, num_trials) %>%
    distinct()
```

Histogram of main outcome variable --> Correct on 2-AFC measure

```{r}
qplot(x=correct, data=df)
```

Histogram rt just to make sure nothing weird is going on 

```{r}
qplot(x=rt, data=df)
```

## Flag and filter bad RTs

```{r}
df <- df %>%
    filter(id != "NA") %>% 
    mutate(include_good_rt = ifelse(log(rt) > mean(log(rt)) + 2 * sd(log(rt)) |
                                        log(rt) < mean(log(rt)) - 2 * sd(log(rt)),
                                    "exclude", "include"))

df %>% group_by(include_good_rt) %>% summarise(n())

df <- filter(df, include_good_rt == "include")
```

### Main analysis

Plot accuracy for each gate within each sign.

```{r, cache = T}
ms <- df %>%
    na.omit() %>% 
    group_by(gate_name, gate_num, gate_signer, gate) %>%
    summarise(mean_correct = mean(correct),
              ci_h = ci.high(correct),
              ci_l = ci.low(correct))
```

Now plot

```{r, fig.height=12, fig.width=10}
qplot(x=gate_num, y=mean_correct, color = gate_signer, data=ms) +
    facet_wrap( ~ gate_name,ncol=10) +
    geom_line() +
    geom_pointrange(aes(ymin=mean_correct - ci_l, 
                        ymax=mean_correct + ci_h), 
                    width = .05, size=0.6) +
    geom_hline(y=0.5, lty="dashed") +
    theme_bw()
```

### Compute empirical F0

Decisions about gate were made by VM/KM. Decision criteria was as follows:
- Earliest gate that achieved accuracy above chance

Note: there were some signs that did not have a clear gate based on the data. 
In these cases we stick with the experimenter defined F0. 

```{r}
#grab gate names
df_empricial_f0 <- ms %>% 
    ungroup() %>% 
    select(gate_name) %>% 
    unique()

# create vector with gate decisions 
gate_decision <- c(4, 5, 3, 4, 1, 4, 5, 5, 4, 1, 4, 5, 2, 6, 6, 
                    4, 4, 5, 3, 6, 5, 2, 3, 6, 5, 3, 5, 4, 6, 6, 6, 
                    5, 4, 3, 3, 3, 6, 4)
# check length: should be 38
length(gate_decision)

# bind to gate names 
df_empricial_f0 %<>% cbind(gate_decision)
```

Take the gate decisions and add this information to the larger summarized data frame: ms.
Then only keep the gates where there is a match between gate_decision and gate_num variables.

```{r}
ms_gate_decisions <- ms %>% 
    left_join(y = df_empricial_f0, by = "gate_name") %>%
    ungroup() %>% 
    select(gate_name, gate_num, gate, gate_decision) %>% 
    filter(gate_decision == gate_num)
```

Extract the frame information from the gate variable. And convert to ms.

```{r}
regexp <- "[[:digit:]]"

str_locate(ms_gate_decisions$gate, regexp)[1]

ms_gate_decisions %<>% 
    select(gate, gate_decision) %>% 
    mutate(
        f0_sec = as.numeric(str_extract(gate, regexp)),
        f0_frame = as.numeric(str_sub(gate, 
                           start = str_length(gate) - 3, 
                           end = str_length(gate) - 2)),
        f0_tot_frames = (f0_sec * 30) + f0_frame,
        f0_ms_1 = f0_tot_frames * 33,
        f0_ms_2 = (f0_sec * 1000) + (f0_frame * 33)
    )
```

Save data frame, so we can add the experimenter chosen F0

```{r}
# write.csv(x = ms_gate_decisions, "sol-empirical-gate-decisions.csv", row.names = F)
```

Read in data frame with experimenter F0 added and compute the difference for each sign
and the average difference overall. 

```{r}
df_final <- read.csv("sol-empirical-gate-decisions.csv")
```

```{r, echo = F}
df_final %<>%
    dplyr::mutate(
        f0_diff_empirical_experiment_1_ms = abs(f0_experimenter - f0_ms_1),
        f0_diff_empirical_experiment_2_ms = abs(f0_experimenter - f0_ms_2),
        f0_diff_empirical_experiment_1_frames = round(abs(f0_experimenter - f0_ms_1) / 33),
        f0_diff_empirical_experiment_2_frames = round(abs(f0_experimenter - f0_ms_2) / 33)
    )
```

Summarise how far off we were. First we compare the difference between empirical and experiment, if we use the following computation to get F0

$frames * 33$

```{r, echo = F}
ms_diff <- df_final %>% 
    summarise(
        min_diff_ms = min(f0_diff_empirical_experiment_1_ms),
        max_diff_ms = max(f0_diff_empirical_experiment_1_ms),
        min_diff_frames = min(f0_diff_empirical_experiment_1_frames),
        max_diff_frames = max(f0_diff_empirical_experiment_1_frames),
        avg_diff_ms = mean(f0_diff_empirical_experiment_1_ms),
        avg_diff_frames = mean(f0_diff_empirical_experiment_1_frames)
    )

knitr::kable(ms_diff, digits=2)
```

Now we compare the difference if we use the following computation to get F0: 

$(seconds * 1000) + (frames * 33)$

```{r, echo = F}
ms_diff_2 <- df_final %>% 
    summarise(
        min_diff_ms = min(f0_diff_empirical_experiment_2_ms),
        max_diff_ms = max(f0_diff_empirical_experiment_2_ms),
        min_diff_frames = min(f0_diff_empirical_experiment_2_frames),
        max_diff_frames = max(f0_diff_empirical_experiment_2_frames),
        avg_diff_ms = mean(f0_diff_empirical_experiment_2_ms),
        avg_diff_frames = mean(f0_diff_empirical_experiment_2_frames)
    )

knitr::kable(ms_diff_2, digits=2)
```

```{r}
ggplot2::qplot(f0_diff_empirical_experiment_2_frames, data = df_final,
               binwidth = 0.5) + 
    ylim(0, 8) +
    scale_x_continuous(limits = c(0, 8), breaks=0:8) +
    theme_bw()
```