---
title: "sol-munging"
author: "Kyle MacDonald"
date: "June 12, 2015"
output: html_document
---

## Script to munge sol eye movement data

```{r}
rm(list=ls())
```

```{r}
source("../analysis/helpers/libraries_v_3.6.R")
library(dplyr)
library(stringr)
```

### Read in icharts for V1 and V2 

```{r}
v1_df <- readiChart("raw_data/sol-eye-movements/sol-ichart-v1-post-gating.txt")
v2_df <- readiChart("raw_data/sol-eye-movements/sol-ichart-v2-post-gating.txt")
```

### Add variable to track stimuli 

```{r}
v1_df$stimuli <- "V1"
v2_df$stimuli <- "V2"
```

### Make sure that all columns with eye-tracking data are character class

Not totally sure why the readiChart function doesn't read all of these as characters (?)

```{r}
# first we grab the first/last columns that are class logical 
start_col <- grep("4900", colnames(v1_df))
end_col <- grep("5033", colnames(v1_df))

# now we can change the class for each column 
v1_df[, start_col:end_col] <- as.character(unlist(v1_df[, start_col:end_col]))
```

### Bind data frames together

```{r}
v1_v2_df <- bind_rows(v1_df, v2_df)
```

### Change F. in column name to - (codes for looking behavior before F0; noun onset)

```{r}
colnames(v1_v2_df) <- sapply(colnames(v1_v2_df), function (x) {
    str_replace(x, "F\\.", "-")  
})
```

One child completed two PEEKs because the fire alarm went off after first 8 trials in PEEK1 – here, we read in the data as two subjects (30036 and 99999) and now we revalue subject 99999 to be 30036.

After running this, 30036 should have 22 vanilla trials and 99999 should no longer exist.

```{r}
v1_v2_df$Sub.Num[v1_v2_df$Sub.Num == "99999"] <- "30036" 
```

### Save final/merged data frame

```{r, eval = F}
write.csv(v1_v2_df, file = "sol-ichart-merged-post-gating.csv", row.names = F, na = "NA")
```