---
title: "sol-gating-import"
author: "Kyle MacDonald"
date: "April 27, 2015"
output: html_document
---

#### Import SOL-gating Data

Script to munge ipad data for sol-gating experiment. 


Load libraries for data manipulation

```{r load_libraries, warning=FALSE, message=FALSE}
rm(list=ls()) 
library(plyr)
library(dplyr)
library(stringr)
setwd("../../raw_data/sol-gating/")
```

Read in data

```{r read in version 2 data}
all.data <- as.data.frame(matrix(ncol = 0, nrow = 0))

#grab all file names from data dir. 
all_results <- list.files(pattern="*.txt")

#function to munge the data
#takes in a list of filenames (.txt of each sub's data), 
#strips html escape characters, and grabs the relevant info for each trial
#returns data frame with all the data

gating_import <- function(filename) {
        x <- readLines(filename, warn=FALSE)
        x <- unlist(strsplit(x,'<li>'))
        
        #grab id
        regexp <- "[[:digit:]]+" # extract just numbers
        id <- x[2067]
        id <- str_extract(id, regexp)
        id <- as.numeric(id)

        #strip html characters
        x <- gsub('\\"',"", x)
        x <- gsub("\\\\\"","",x)
        x <- gsub("</li>","",x)
        x <- gsub("</ul>\\},\\{<ul>","",x)
        x[length(x)] <- gsub("</ul>\\}]","",x[length(x)])
        x <- gsub("^.*?: ","",x)
        x <- gsub("</ul>}]","",x)
        
        #grab date 
        date <- str_sub(filename,20,36)
        date <- gsub('_','',date)
        date <- gsub('\\.','',date)
        
        # grab other sub info
        gender <- x[2058]
        age <- x[2057]
        asl_fluency <- x[2059]
        age_learned_asl <- x[2060]
        
         # grab trial information 
        x <- x[5:2056]
        
        #bind to data frame
        x <- as.data.frame(matrix(x,nrow=length(x),ncol=9,byrow=TRUE), 
                           stringsAsFactors=F)
        x$V10 <- date
        x$V11 <- id
        x$V12 <- gender
        x$V13 <- age
        x$V14 <- asl_fluency
        x$V15 <- age_learned_asl
        return(unique(x)) ## need this to get the data frame!
}

#apply munging function to each kid's data file
all.data <- ldply(.data = all_results, .fun = gating_import)

#add variable names to columns
names(all.data) <- c("trial","trial_in_block","block","gate","target_image",
              "chosen_image","chosen_img_index","correct","rt","date", "id",
              "gender", "age", "asl_fluency", "age_learned_asl")
```

Chop up gate filename, so we can analyze each timeslice (1-6) for 
each gate. 

```{r}
# extract string from long ugly gate name
gate_extract <- function (gate_name) {
    regexp <- "[[:digit:]]"
    #locate the first digit in string
    digit_idx <- str_locate(gate_name, regexp)
    digit_idx <- as.numeric(digit_idx[1])
    # grab everything before the first digit in the string
    gate <- str_sub(gate_name, 1, digit_idx)
    return(gate)
}

gates <- sapply(all.data$gate, function (x) gate_extract(x))

# remove NAs
gates <- gates[!is.na(gates)]

# add to data frame
all.data$gate_name <- gates

# revalue following gates
# "bear_where_2" --> "bear_where_1"
# "bird_where_2" --> "bird_where_1"
# "doll_where_4" --> "doll_where_3"

all.data$gate_name<- revalue(all.data$gate_name, 
                             c("p_bear_where_2" = "p_bear_where_1",
                               "p_bird_where_2" = "p_bird_where_1",
                               "r_doll_where_4" = "r_doll_where_3",
                               "p_bear_look_2" = "p_bear_look_1",
                               "p_shoe_hey_3" = "p_shoe_hey_2",
                               "p_doll_find_2" = "p_doll_find_1",
                               "r_book_which_2" = "r_book_which_1",
                               "r_car_which_2" = "r_car_which_1",
                               "r_cat_where_4" = "r_cat_where_3",
                               "r_shoes_where_4" = "r_shoes_where_3"))
```

Now that we have separated the gate name, we need to get the number
of the gate (1-6).

```{r}
# get gate numbers
gate_nums <- as.vector(sapply(all.data$gate, function (x)
    substr(x, str_length(x), str_length(x))))

# add to data frame
all.data$gate_num <- gate_nums

# change correct to logical 
all.data$correct <- as.logical(all.data$correct)
```

Extract the signer initial from front of gate

```{r}
all.data$gate_signer <- as.vector(sapply(all.data$gate, function (x)
    substr(x, 1, 1)))

all.data$gate_signer <- as.factor(all.data$gate_signer)
```

Check the number of gates for each sign

```{r}
gate_df <- all.data %>%
    group_by(gate_name) %>%
    summarise(num_gates = n()) %>% 
    print()
```

Save output

```{r}
write.csv(all.data, file = "../../analysis/gating/sol_gating_processed-df.csv", row.names=F)
```

